---
title: "Pediatric Asthma Hospitalizations Across Texas Counties"
author: "Abhinav Sripathi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(gt)
source("Rcode_v1.R")
```

# Project Overview

This project examines pediatric asthma hospitalizations across Texas counties in 2019 using Texas PUDF inpatient data.

# Figure 1. Texas County Map

```{r}
p_map
```

# Table 1. Top 10 Counties by Pediatric Asthma Hospitalizations

```{r}
gt::gt(top10_table)
```

# Figure 2. Quarterly Pediatric Asthma Hospitalizations

```{r}
p_quarter
```

# Table 2. Validation Against All-Age Asthma Hospitalizations

```{r}
gt::gt(top10_validation)
```

# Key Findings

- Pediatric asthma hospitalizations varied across Texas counties.
- Harris County had the highest number of pediatric asthma hospitalizations among Texas counties in 2019.
- Pediatric counts were validated against all-age asthma hospitalization counts.
